Meta-analysis of fungicide application timing experiments for powdery mildew

### 2020-05-22 01_Meta-analysis_experiments.Rmd
wordsmithing in chapter 2, fix incorrect reference for NGA and delete  temp file

@@

**2001 - 2004 trials**  
Trial data were obtained from a non-published manuscript.  
Ratings for powdery mildew were on a 1-5 rating scale and can be read in the
file "Powdery mildew paper#1.doc".  
Comparing trials which have not used the same rating scale will be done using a
percentage change.

**2013 Field trials**  
Trials were conducted by the National Growers Alliance (NGA). The raw data were
obtained from Lawrie Price. NGA data were formatted to be compliant with
existing data rating and scales in the R script `Cleaning historical data.R`.

@@

```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}
PM.dat <- import_data()

kable(
   PM.dat %>%
      group_by(
         trial_ref,
         year,
         location,
         trial_design,
         replicates,
         planting_date,
         emergence_date,
         first_sign_disease
      ) %>%
      summarise(treatments = length(n_treatment)),
   caption = "Description of Experiments"
)  %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   scroll_box(width = "900px", height = "500px")
```

@@

   1. No powdery mildew colonies observed on any plant  
   2. Small colonies in lower 1/3 of canopy, up to 75% of plants affected  
   3. Colonies in lower 1/2 of canopy, >75% of plants affected  
   4. Colonies in lower 2/3 of canopy, up to 75% of plants affected  
   5. Colonies in lower 2/3 of canopy, >75% of plants affected  
   6. Colonies in lower 2/3 of canopy, 100% of plants affected  
   7. Colonies in lower 2/3 of canopy of 100% of plants, some plants with colonies also in top 1/3 of canopy  
   8. Colonies to top of plant with >75% of plants affected  
   9. Colonies to top of plant with 100% of plants affected and heavy leaf drop

## Experimental locations

Experimental locations where data was sufficient to include in meta-analysis.

```{r Experiment_locations}
experiment_sites <- data.frame(
   location = c(
      "Hermitage Research Station",
      "Red Vale & Kingaroy Research Station",
      "Gatton",
      "Emerald Agricultural College",
      "Bongeen 1 & 2",
      "NGA - Premer",
      "NGA - Millmerran",
      "NGA - Marys Mount",
      "NGA - Goolhi",
      "Missen Flats",
      "Wellcamp"
   ),
   lat = c(
      -28.215 ,
      -26.58,
      -27.56,
      -23.54,
      -27.51666,
      -31.43449,
      -27.923674,
      -31.0142,
      -31.00246,
      -27.905313,
      -27.564277
   ),
   lon = c(
      152.1003,
      151.83,
      152.32,
      148.19,
      151.450,
      150.0052,
      151.242706,
      150.05018,
      149.82507,
      151.9772,
      151.867879
   )
)

>>>>

Studies were conducted in the following locations and years and were considered for inclusion in this analysis.

@@

**2001 - 2004 trials**  
Trial data were obtained from a non-published manuscript.  
Ratings for powdery mildew were on a 1-5 rating scale and can be read in the file "Powdery mildew paper#1.doc".
Comparing trials, which have not used the same rating scale will be done using a percentage change.

**2013 Field trials**  
Trials were conducted by the [Northern Growers Alliance (NGA)](https://www.nga.org.au/).
The raw data were obtained from Lawrie Price.
NGA data were formatted to be compliant with existing data rating and scales using the R script [`R/Cleaning historical data.R`](https://github.com/openplantpathology/Mungbean_PM/blob/master/R/Cleaning%20historical%20data.R).

@@

```{r data_summary, echo=FALSE, message=FALSE, warning=FALSE}
PM.dat <- import_data()

kable(
   PM.dat %>%
      group_by(trial_ref, ) %>%
      summarise(
         year = unique(year),
         location = unique(location),
         mean_treat_replicates = mean(replicates),
         planting_date = unique(planting_date),
         first_sign_disease = unique(first_sign_disease),
         treatments = length(n_treatment)
      ) %>%
      arrange(year),
   caption = "Description of Experiments"
)  %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   scroll_box(width = "900px", height = "500px")
```

@@

   1. No powdery mildew colonies observed on any plant

   2. Small colonies in lower 1/3 of canopy, up to 75% of plants affected

   3. Colonies in lower 1/2 of canopy, >75% of plants affected

   4. Colonies in lower 2/3 of canopy, up to 75% of plants affected

   5. Colonies in lower 2/3 of canopy, >75% of plants affected

   6. Colonies in lower 2/3 of canopy, 100% of plants affected

   7. Colonies in lower 2/3 of canopy of 100% of plants, some plants with colonies also in top 1/3 of canopy

   8. Colonies to top of plant with >75% of plants affected

   9. Colonies to top of plant with 100% of plants affected and heavy leaf drop

## Experiment locations

The following map displays experiment locations where data was sufficient to include in this meta-analysis.

```{r Experiment_locations, echo=FALSE}
experiment_sites <- data.frame(
   location = c(
      "Hermitage Research Station",
      "Red Vale & Kingaroy Research Station",
      "Gatton",
      "Emerald Agricultural College",
      "Bongeen 1 & 2",
      "NGA - Premer",
      "NGA - Millmerran",
      "NGA - Marys Mount",
      "NGA - Goolhi",
      "Missen Flats",
      "Wellcamp"
   ),
   lat = c(
      -28.215 ,
      -26.58,
      -27.56,
      -23.54,
      -27.51666,
      -31.43449,
      -27.923674,
      -31.0142,
      -31.00246,
      -27.905313,
      -27.564277
   ),
   lon = c(
      152.1003,
      151.83,
      152.32,
      148.19,
      151.450,
      150.0052,
      151.242706,
      150.05018,
      149.82507,
      151.9772,
      151.867879
   )
)
